Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-06 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:06	10:17:51	(Thu 6.Aug)

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR. A 40x40 pixel group from shadow, highlight and speckle were chose, and the window responses from each pixel plotted on top of each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe level of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. Full opening angle. Parameters. }\label{mvdr_selected_windows}
\end{figure*}

>>>>

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR. The image is of the oiltanker Holmengraa, reconstructed from the 32 element HISAS1030 sonar, operated in ssectorscan mode with an oversampling factor of ~10. The window responses was computed from 40x40 pixel groups in the shadow, highlight and speckle region. The dashed red lines at -13dB and -43dB marks the peak sidelobe level of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. Full opening angle. Parameters. }\label{mvdr_selected_windows}
\end{figure*}
